Carryover effects in free recall reveal how prior experiences influence memory for new experiences

### 2022-12-23 paper/main.tex
backing up initial attempts at introduction

% the role of context and prior experience in memory

% situation models: forming expectations, predicting ambiguous future experiences

@@

\bibliographystyle{apa}
\bibliography{cdl}
\end{document}

>>>>

% the role of context and prior experience in memory
Experience is subjective: different people who encounter identical physical experiences
can take away very different meanings and memories.  One reason is that our subjective
experiences in the moment are shaped in part the idiosyncratic prior experiences, memories,
goals, thoughts, expectations, and emotions that we bring with us into the present moment.
These factors collectively define a \textit{context} for our experiences~\citep{Mann20}.

% situation models: forming expectations, predicting ambiguous future experiences
The contexts we encounter help us to construct \textit{situation models}~\citep{RangRitc12, MannEtal15}
or \textit{schemas}~\citep{MasiEtal22, BaldEtal18} that describe how experiences are likely to unfold
based on our prior experiences with similar contextual cues.  For example, when we enter a sit-down restaurant,
we might expect to be seated at a table, given a menu, and served food.  Priming someone
to expect a particular situation or context can also influence how they resolve potentail ambiguities
in their ongoing experiences, including ambiguous movies and narratives~\citep{YeshEtal17}.

@@

\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
\end{document}
